\documentclass[letterpaper,12pt]{article}

\usepackage{fullpage}
\usepackage{parskip}

\usepackage{color}
\definecolor{pink}{RGB}{240,109,169}
\definecolor{brown}{RGB}{99,59,27}

\usepackage{enumitem}
\setlist[description]{font=\normalfont\bfseries}

\usepackage{titlesec}
\titleformat{\section}{\bfseries\large}{}{0pt}{}
\titleformat{\subsection}{\bfseries\normalsize}{}{0pt}{}

\pagenumbering{gobble}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}

  \section{What to Eat and See}

    \subsection{Near North Side}
    This is the neighborhood around Holy Name Cathedral.

    \begin{description}\setlength{\itemsep}{0pt}
      \item[Eataly, 43 E Ohio St.]
              Two floors and 23 eateries devoted to Italian food. If you
              stay in this neighborhood for lunch, you really ought to
              consider eating here.
      \item[John Hancock Center, 875 N Michigan Ave.]
              Enjoy views of Chicago from the lounge on the 96th floor.
      \item[Museum of Contemporary Art Chicago, 220 E Chicago Ave.]
              Small, eclectic exhibitions of post-1945 art. The building
              is architecturally notable.
    \end{description}

    \subsection{The Loop}
    Walk south for about 20 minutes (crossing the river), or take the
    {\color{red} Red Line} from Chicago station to Lake station or
    Monroe station.

    \begin{description}\setlength{\itemsep}{0pt}
      \item[Russian Tea Time, 77 E Adams St at Michigan Ave.]
              Full afternoon tea service with Russian food.
      \item[Pierogi Heaven, 169 N Wells St at W Lake St.]
              Inexpensive and delicious pierogis made with a variety of
              fillings. No service or atmosphere -- you order at the
              counter and get your food on a plastic plate. This is our
              favorite quick takeout restaurant.
      \item[Millenium Park, along Michigan Ave south of Randolph St.]
              Enjoy the public space, views of the Chicago skyline, and
              landmark artworks \emph{Cloud Gate} (``the Bean'') and
              \emph{Crown Fountain}.
      \item[The Art Institute of Chicago, 111 S Michigan Ave at Adams St.]
              The second largest art museum in the United States.
    \end{description}

    \subsection{West Town}
    Take the {\color{red} Red Line} from Chicago station to Lake
    station, then transfer through the underground pedestrian mall to
    the Washington station on the {\color{blue} Blue Line}. Take the
    {\color{blue} Blue Line} to the Damen station.

    \begin{description}\setlength{\itemsep}{0pt}
      \item[Big Star, 1531 N Damen Ave, just south of the Damen station.]
              Excellent beer and liquor selection, tacos, and (always
              crowded) outdoor seating. Cash only.
      \item[Dimo's Pizza, 1615 N Damen Ave., just north of the Damen station.]
              Good beer selection and pizzas with unusual toppings, like
              chicken and waffles or macaroni and cheese.
      \item[Myopic Books, 1564 N Milwaukee Ave, southeast from the Damen station.]
              Three creaky floors packed full of used books and
              hipsters.
      \item[Wormhole Coffee, 1462 N Milwaukee Ave., southeast from the Damen station.]
              A hip coffee shop that has a DeLorean time machine parked
              inside.
    \end{description}

    \subsection{Lower West Side}
    Take the {\color{red} Red Line} from Chicago station to Lake
    station, then exit to street level and transfer to the elevated
    tracks for the {\color{pink}Pink Line}. Take the {\color{pink} Pink
    Line} to the 18th Street station in Pilsen.

    \begin{description}\setlength{\itemsep}{0pt}
      \item[National Museum of Mexican Art, 1852 W 19th St in Harrison Park.]
              One of the most prominent institutions for Mexican art in
              the United States.
      \item[Many eateries along 18th St.] Wander around, eat really good food.
    \end{description}

    \subsection{Near West Side}
    Take the {\color{red} Red Line} from Chicago station to Lake
    station, then exit to street level and transfer to the elevated
    tracks for the {\color{green}Green Line}. Take the {\color{green}
    Green Line} to the Morgan-Lake station.

    \begin{description}\setlength{\itemsep}{0pt}
      \item[Little Goat Diner, 820 W Randolph St at Green St.]
              A well-known lunch spot that serves fun variations on
              comfort food. Expect to wait for a table.
      \item[Glazed and Infused Doughnuts, 813 W Fulton Market at Green St.]
              Fancy doughnuts.
      \item[Publican Quality Meats, 825 W Fulton Market at Green St.]
              A butcher shop and caf\'{e} that serves house-made
              charcuterie, aged meats, artisanal cheeses, freshly-baked
              breads, and sandwiches made with these ingredients.
    \end{description}

  \hrulefill

  \section{Reminder}

  The evening celebration will be at {\bfseries Farmhouse, 228 W Chicago
  Ave}. The restaurant is five blocks west of the cathedral at the
  intersection with N Franklin St and right next to the Chicago station
  on the {\color{brown}Brown Line}.

  Festivities will begin at 7pm with a cocktail hour on the upper floor
  of the restaurant. At 8pm, dinner will be served, and both floors of
  the restaurant will be open to our party until 11pm.

  We hope that you enjoy your afternoon and look forward to the evening
  celebration with you!

  \hfill --- Hana and Steve

\end{document}
